Drivers of sex differences in consumption (NAMCS)

### 2017-07-20 sex-difference/sex-namcs.Rmd
sex diff totals
updates

sex_codes = read_tsv('namcs_sex_codes.tsv') %>%
  rename(dx=code)

dx = read_tsv_years('../../db/namcs/data/namcs_dx_%i.tsv') %>%
  left_join(sex_codes, by='dx')

dx_visit = dx %>%
  group_by(visit_id) %>%
  summarize(uti='uti' %in% diagnosis_type,
            acne='acne' %in% diagnosis_type,
            arc='acute_rc' %in% diagnosis_type)

@@

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(dx_visit, by='visit_id') %>%
  replace_na(list(uti=FALSE, acne=FALSE, arc=FALSE)) %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') %>%
  mutate_at(top_abx$abx, function(x) if_else(is.na(x), 0L, x))

@@

@@

```{r}
svytable(~sex+uti, adult_design) %>%
  as_data_frame() %>%
  mutate(n=mpy(n)) %>%
  kable
```

@@

```{r}
svytable(~sex+arc, adult_design) %>%
  as_data_frame() %>%
  mutate(n=mpy(n)) %>%
  kable
```

>>>>

dx_codes = read_tsv('../../data/fd_codes.tsv') %>%
  rename(dx=code, desc=dx_desc)

diagnosis_types = unique(dx_codes$diagnosis_type)

dx = read_tsv_years('../../db/namcs/data/namcs_dx_%i.tsv') %>%
  left_join(dx_codes, by='dx')

@@

visits = read_tsv_years('../../db/namcs/data/namcs_visits_%i.tsv') %>%
  mutate(age_group=case_when(.$age <= 19 ~ 'child',
                             .$age <= 64 ~ 'adult',
                             .$age <= 92 ~ 'elderly')) %>%
  left_join(n_abx, by='visit_id') %>% replace_na(list(n_abx=0)) %>%
  left_join(abx_visit, by='visit_id') %>%
  mutate_at(top_abx$abx, function(x) if_else(is.na(x), 0L, x))

@@

## Diagnoses across the sexes

What's the difference in primary diagnoses across the sexes? I look in not-children.

```{r diagnoses}
unique_primary_dx = dx %>%
  filter(dx_number==1) %>%
  left_join(visits, by=c('visit_id', 'year')) %>%
  filter(age_group != 'child') %>%
  count(dx, sort=TRUE) %>%
  head(20) %$%
  dx

unique_primary_dx
```

```{r}
f = function(code) {
  filter(dx, dx_number==1, dx==code) %>%
    mutate(n_dx=1) %>%
    left_join(visits, by=c('visit_id', 'year')) %>%
    replace_na(list(n_dx=0)) %>%
    design_f() %>%
    subset(age_group != 'child') %>%
    svyby(~n_dx, ~sex, design=., svytotal) %>%
    as_data_frame() %>%
    mutate(code=code)
}

dx_by_sex = lapply(unique_primary_dx, f) %>% bind_rows()
dx_by_sex
```

```{r}
dx_by_sex %>%
  rename(n=n_dx) %>%
  mutate(ci=1.96*se, ci_low=n-ci, ci_high=n+ci) %>%
  select(code, sex, n, ci_low, ci_high) %>%
  gather('key', 'value', n:ci_high) %>%
  mutate(key=case_when(.$sex=='male' & .$key=='n' ~ 'x',
                       .$sex=='male' & .$key=='ci_low' ~ 'xmin',
                       .$sex=='male' & .$key=='ci_high' ~ 'xmax',
                       .$sex=='female' & .$key=='n' ~ 'y',
                       .$sex=='female' & .$key=='ci_low' ~ 'ymin',
                       .$sex=='female' & .$key=='ci_high' ~ 'ymax')) %>%
  select(-sex) %>%
  spread(key, value) %>%
  ggplot(aes(x=x, xmin=xmin, xmax=xmax, y=y, ymin=ymin, ymax=ymax, label=code)) +
  geom_abline(col='gray') +
  geom_point() + geom_errorbar() + geom_errorbarh() + geom_text() +
  coord_fixed() +
  theme_minimal()
```

```{r}
g = function(diagnosis_type) {
  filter(dx, dx_number==1, diagnosis_type==diagnosis_type) %>%
    mutate(n_dx=1) %>%
    left_join(visits, by=c('visit_id', 'year')) %>%
    replace_na(list(n_dx=0)) %>%
    design_f() %>%
    subset(age_group != 'child') %>%
    svyby(~n_dx, ~sex, design=., svytotal) %>%
    as_data_frame() %>%
    mutate(diagnosis_type=diagnosis_type)
}

#dt_by_sex = lapply(diagnosis_types, f) %>% bind_rows()
#dt_by_sex
g('pneumonia')
```

@@

```{r, eval=FALSE}
svytable(~sex+uti, adult_design) %>%
  as_data_frame() %>%
  mutate(n=mpy(n)) %>%
  kable
```

@@

```{r, eval=FALSE}
svytable(~sex+arc, adult_design) %>%
  as_data_frame() %>%
  mutate(n=mpy(n)) %>%
  kable
```

## Overall consumption

How many antibiotic prescriptions total were made by each sex?

```{r overall_abx}
svyby(~n_abx, ~sex, svytotal, design=adult_design)
```
